\section{Our Long Output Scheme}

Here we describe the scheme between the classical client and an honest quantum server. This is similar to the underlying construction of \cite{mahadev_delegation}. We first preprocess the circuit using tools such as \cite{quant-ph/0301040}. We then follow \cite{kitaev2002classical} to reduce the problem to an instance of local Hamiltonian. Using tools from \cite{PhysRevA.93.022326}, the local Hamiltonian is written in a simple form. Then, NYI cuz we're stuck. \hannote{be more explicit}

We pick our universal gate set to be Hadamard gate and controlled phase gate following \cite{quant-ph/0301040}:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
Which is proven to be universal in \cite{kitaev_1997}.

\subsection{Preprocessing circuit}

In order to estimate the energy of a Hamiltonian using only $X$ and $Z$ measurements, the gates in the circle must be combinations of $X$ and $Z$ matrices. To begin, we apply a transformation to the circuit to use only real states and gates. This transform is taken from \cite{quant-ph/0301040}.

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$. The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

\begin{proof}

Consider the transform on quantum states
	$$\mathcal{F}(\ket{\phi})=(\Re\ket{\phi})\otimes\ket{0}+(\Im\ket{\phi})\otimes\ket{1}$$
where $\Re$ and $\Im$ denote real and imaginary parts respectively.

This transform commutes with Hadamard gates on the respective qubit. On the other hand, exchanging $\mathcal{F}$ with a controlled phase gate turn it into a combination of Hadamard and Toffoli gates. Mathematically,
$$\mathcal{F}\circ H_s=H_s\circ\mathcal{F}$$
$$\mathcal{F}\circ\Lambda_f(P(i)_s)=\Lambda^2_{f,s}(X_0Z_0)\circ\mathcal{F}=\Lambda^2_{f,s}(X_0)H_0\Lambda^2_{f,s}(X_0)H_0\circ\mathcal{F}$$

We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
\begin{itemize}
	\item $C'$ uses only Hadamard and Toffoli gates.
	\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
	\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
\end{itemize}
\end{proof}

We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
\end{definition}

\begin{theorem}
	$H,\Lambda^2(X)\in\spn\mathcal{G}_{XZ}$ with $O(1)$ nonzero components.
\end{theorem}

\begin{proof}
	$$H=\frac{1}{\sqrt{2}}(X+Z)$$
	$$\Lambda^2_{1,2}(X_3)=\ket{11}\bra{11}\otimes X+(I-\ket{11}\bra{11})\otimes I$$
	$$\ket{11}\bra{11}=\frac{1}{4}(I\otimes I+Z\otimes Z-I\otimes Z-Z\otimes I)$$
\end{proof}

\subsection{Constructing a local Hamiltonian instance}

Here we reduce a circuit into a local Hamiltonian instance with a few additional properties.

\begin{theorem}
	Let $C=U_T\ldots U_1$ where $U_i$ are either $H$ or $\Lambda^2(X)$, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time a local Hamiltonian instance $H_{circuit}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{circuit}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{circuit}|H_{circuit}|\psi_{circuit}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{circuit}}=0\Rightarrow\braket{\phi|H_{circuit}|\phi}\geq\frac{3}{4}$
		\item $H_{circuit}\in\spn\mathcal{G}_{XZ}$, with $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

\begin{proof}
	We construct the Hamiltonian by ensuring states perpendicular to $\ket{\psi_{circuit}}$ have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification to $\spn\mathcal{G}_{XZ}$ is taken from \cite{PhysRevA.78.012352}.

Let $x_i$ denote the $i$-th bit of $x$, and let $n$ be the number of qubits in $C$.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
As a sum of projections, clearly $H_{clock}\geq 0$. We shall also show that $H_{clock}\in\spn\mathcal{G}_{XZ}$.
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

Then, we ensure that the initial condition is set up correctly.
$$H_{in}=\sum_{i=1}^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, $H_{in}\in\spn\mathcal{G}_{XZ}$
$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$

Then, we ensure that the gates are applied correctly.
$$H_{prop}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

Next, we check that $H_{prop}\geq0$ by the following transform.

$$W=\sum_{j=0}^L U_j\ldots U_1\otimes\ket{j}\bra{j}$$
$$W^\dagger\phi=\sum_{t=0}^T\ket{x}\otimes\ket{\hat{t}}$$
$$W^\dagger H_{prop} W=
\begin{pmatrix}
	\frac{1}{2} & -\frac{1}{2} & & & &  \\
	-\frac{1}{2} & 1 & -\frac{1}{2} & & & \\
	& -\frac{1}{2} & 1 & \ddots & & \\
	& & \ddots & \ddots & -\frac{1}{2} & \\
	& & & -\frac{1}{2} & 1 & -\frac{1}{2} \\
	& & & & -\frac{1}{2} & \frac{1}{2}
\end{pmatrix}$$

According to \cite{2002quant.ph.10077A}, $H_{prop}\geq 0$ due to the above form being relevant to random walks. Furthermore, the last nonzero eigenvalue of $H_{prop}$ is at least $\frac{1}{2(T+1)^2}$.

We can also write $H=\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
Extra care must be taken for boundary cases.
$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$

To properly combine the three Hamiltonians defined, we consider the kernels of the Hamiltonians we defined.
$$K_{clock}=\ker H_{clock}$$
$$K_{in}=\ker H_{in}$$
$$K_{prop}=\ker H_{prop}$$
It is clear that $K_{clock}$ consists of the states with time registers of the form $\ket{\hat{t}}$.

\begin{lemma}
	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
\end{lemma}

\begin{proof}
	Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now nonsider some $\tilde{t}$ such that $\ket\phi\bra{\tilde{t}}\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\ket\phi\bra{\tilde{t+1}}=U_{t+1}\ket\phi\bra{\tilde{t}}$ for $t\ne T$, and $\ket\phi\bra{\tilde{t}}=U_t\ket\phi\bra{\tilde{t-1}}$ for $t\ne0$. So we can obtain the required statement by induction.
\end{proof}

\begin{corollary}
	$K_{clock}\cap K_{in}\cap K_{prop}=\spn\set{\ket{\psi_{circuit}}}$
\end{corollary}

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{x|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

\subsection{Measuring ground state}

Now we put the above results in term of measurement outputs.

\begin{theorem}\label{ThmXZCheck}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
\end{theorem}
\begin{proof}

Here we follow \cite{PhysRevA.93.022326}.

\begin{algorithm}
	\caption{Check for ground state}
	\begin{algorithmic}[1]
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S=\frac{|d_S|}{D}$
		\State $\tilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\tilde{S}}\gets$ Measure $\ket\phi$ in the $\tilde{S}$ basis
		\If{$\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$}
			\State Accept
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

\begin{align*}
	\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
	&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\E[\lambda_{\tilde{S}}]]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]
\end{align*}

Note that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$.

$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
\begin{align*}
	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
	&=\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}
\end{align*}

\end{proof}

\subsection{Analysis and amplification}

A honest server can then commit copies of the ground state of the Hamiltonian for the classical client to measure. The client would keep a single copy for output, and use the other copies to check whether the computation is done properly. Here we analyze what happens if the server is dishonest. We assume that the verifier can possess qubits and do $X$ and $Z$ measurements, but is classical otherwise.

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, the prover would send the client $n=O(\poly(t))$ copies... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)}$ for $i\ne1$. We now decomposite what the prover sends in this basis.
$$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_q}}$$
We categorize the indices $I$ into three types, based on how many $1$s it contains. First kind contains all $1$s. Second contains so little $1$s that... something something Chernoff bound... And the third kind contains the rest.

\end{proof}

\subsection{Getting the Output}

Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation. Now I would analyze the chances of getting this right, maybe in terms of fidelity or in terms of distance between this measured distribution and the ideal distribution...
